\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2018-09-28 paper/manuscript.tex
addressed the point about the admittedly flawed boilerplate illustration table by making a (hopefully) better one

Members of the public visit municipal government websites for a wide variety of purposes \citet{sandoval2012government}, and with significant regularity. In a survey conducted among a random sample of citizens in the state of Georgia in 2000---nearly two decades ago---found that 25\% of internet users reported visiting a local government website in the previous twelve months \citep{thomas2003new}. Furthermore, the use of a local government website is associated with an individual's perspective on government. \citet{tolbert2006effects} finds that users of local government websites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments. Lastly, in a study of residents of Kansas City, Missouri, \citet{ho2017government} find that participants' perceived quality of the city website is strongly associated with their perceptions of the overall effectiveness of the City's communication with the public.

@@

One of the more subtle aspects of local government is the presence of different types of government structures. Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is a certain degree of variance in where a city's executive authority lies. Unfortunately, we do not have access to information about the type of governments across the breadth of our dataset and therefore cannot explore heterogeneity in the relationship between mayoral partisanship and municipal website contents based on the executive system variant. Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor. \citep{Gerber2011a}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities (on a sample of large cities, for which this information is more easily available), find that the inclusion of this potential confounder does not affect the results. Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S. Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.

@@

%Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{Gerber2011a}. However, this kind of finding is not entirely without precedent in the literature (see \citep{Einstein2015}). Similar to the informed dirichlet model, the structural topic model also finds the emphasis on construction and infrastructure by Republicans - in table \ref{tabSTMINRep}, topics 2, 7 and 8 clearly focus on these issues.\footnote{The first Republican topic in Indiana (library, stream, obj, etc.) is likely an artifact from incorrectly converted HTML, and since it presumably only happens only in one Republican city, the topic is classified as very Republican.}

>>>>

Members of the public visit municipal government websites for a wide variety of purposes \citet{sandoval2012government}, and with significant regularity. In a survey conducted among a random sample of citizens in the state of Georgia in 2000---nearly two decades ago---found that 25\% of internet users reported visiting a local government website in the previous twelve months \citep{thomas2003new}. Furthermore, the use of a local government website is associated with an individual's perspective on government. \citet{tolbert2006effects} find that users of local government websites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments. Lastly, in a study of residents of Kansas City, Missouri, \citet{ho2017government} find that participants' perceived quality of the city website is strongly associated with their perceptions of the overall effectiveness of the City's communication with the public.

@@

One of the more subtle aspects of local government is the presence of different types of government structures. Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is a certain degree of variance in where a city's executive authority lies. Unfortunately, we do not have access to information about the type of governments across the breadth of our dataset and therefore cannot explore heterogeneity in the relationship between mayoral partisanship and municipal website contents based on the executive system variant. Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor. \citep{gerber2011mayors}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities (on a sample of large cities, for which this information is more easily available), find that the inclusion of this potential confounder does not affect the results. Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S. Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.

@@

%Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{gerber2011mayors}. However, this kind of finding is not entirely without precedent in the literature (see \citep{Einstein2015}). Similar to the informed dirichlet model, the structural topic model also finds the emphasis on construction and infrastructure by Republicans - in table \ref{tabSTMINRep}, topics 2, 7 and 8 clearly focus on these issues.\footnote{The first Republican topic in Indiana (library, stream, obj, etc.) is likely an artifact from incorrectly converted HTML, and since it presumably only happens only in one Republican city, the topic is classified as very Republican.}

### 2018-09-28 paper/tables/tabBoilerplateIllustration.tex
fixed the same issue for table 7 and removed the last few @markus from the manuscript
moved Table 7
addressed the point about the admittedly flawed boilerplate illustration table by making a (hopefully) better one

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Sat Jul 28 20:51:59 2018
\begin{table}[ht]
\centering
\begingroup\small
\begin{tabular}{lrr}
  \hline
Line & Substantive & Boilerplate \\ 
  \hline
have questions & 0.00 & 1.00 \\ 
  stay connected & 0.00 & 1.00 \\ 
  accident or injury & 0.00 & 1.00 \\ 
  fire damaged buildings & 0.00 & 1.00 \\ 
  gas connections & 0.00 & 1.00 \\ 
  harboring of vagrants & 0.00 & 1.00 \\ 
  roof system problem & 0.00 & 1.00 \\ 
  violation plat note & 0.00 & 1.00 \\ 
  violation setback & 0.00 & 1.00 \\ 
  violation site plan & 0.00 & 1.00 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest probabilities of being classified as boilerplate.} 
\end{table}

>>>>

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Fri Sep 28 17:14:46 2018
\begin{table}[ht]
\centering
\begingroup\small
\begin{tabular}{rl}
  \hline
Boilerplate Probability & Text \\ 
  \hline
1.00 & ri ng h i l \\ 
  1.00 & any others \\ 
  1.00 & premium for \\ 
  1.00 & ra tr \\ 
  1.00 & oa od \\ 
  1.00 & te pos \\ 
  1.00 & design to \\ 
  1.00 & i pli \\ 
  1.00 & wherever possible \\ 
  1.00 & public nuisances \\ 
  1.00 & prime movers \\ 
  1.00 & of the offense \\ 
  1.00 & d nonconformities \\ 
  1.00 & yearshasexceeded costs \\ 
  1.00 & f street \\ 
   \hline
\end{tabular}
\endgroup
\caption{Lines in the corpus of Anchorage, AK, with a probability of 1 of being classified as boilerplate. This table illustrates that lines which get classified as boilerplate largely consist of irrelevant nonsense which needs to be removed.} 
\label{tabBoilerplateIllustration}
\end{table}
